---
title: "ETX0000 Advanced Bean Counting"
---

Brief description of subject

## Learning outcomes

1. learn stuff
2. learn some more stuff
3. use R
4. figure things out

## Teachers

* [**Freda Bloggs**](https://fredabloggs.com). Chief Examiner. Email: [Freda.Bloggs@monash.edu](mailto:Freda.Bloggs@monash.edu)
* [**Harry Xu**](https://harryxu.com). Email: [Harry.Xu@monash.edu](mailto:Harry.Xu@monash.edu)

## References

* [*Advanced R*, 2e](https://adv-r.hadley.nz/) by Hadley Wickham.

```{r}
#| label: load_packages
#| include: false
#| message: false
#| warning: false
#| echo: false
#| cache: false
library(tidyverse)
options(knitr.kable.NA = '')
source(here::here("course_info.R"))
week <- as.integer(1 + ((Sys.Date() - as_date(start_semester))/7))
```

## Weekly schedule

* 2 hour workshop, Wednesdays 9am-11am each week, in Menzies E164.

```{r}
#| label: schedule2
#| message: false
#| warning: false
#| echo: false
#| output: asis
schedule |>
  transmute(
    Date = format(Date + 2, "%d %b"),
    Show = !is.na(Week) & Week <= 12,
    Topic = if_else(!Show, Topic, glue::glue("[{Topic}](./week{Week}/index.html)")),
    #Reference = if_else(!Show, Reference, glue::glue("[{Reference}]({Reference_URL})")),
    Assessments = if_else(is.na(Assignment), Assignment, glue::glue("[{Assignment}]({File})"))
  ) |>
  select(-Show) |>
  knitr::kable(format = "markdown")
```
